Streaming CityJSON datasets

### 2024-05-02 paper/main.tex
Move part of CityJSONSeq can be dbms in the conclusion + merge with cjdb

Furthermore, the CityJSON specification does not prescribe the storage of CityJSONSeq, only the structure of a CityJSONSeq stream (see the five constraints above).
In practice, CityJSONSeq can be stored in a variety of ways, eg in a single file, each feature in a separate file, in a database etc., and the optimal storage solution depends on the implementing application.

@@

While CityJSONSeq was developed mostly for streaming large 3D city datasets, the fact that it has a much lower memory footprint and that it takes an order of magnitude less time to process (for some local operations) makes it an attractive alternative to CityJSON for several use-cases.
For example, CityJSONSeq is used by \emph{cjdb} (a tool for storing CityJSON datasets in a relational database, see \citet{Powalka23}) to store independently one feature per row in the database.
Additionally, in order to facilitate pagination, CityJSONSeq is the return format of the 3DBAG API\footnote{\url{https://api.3dbag.nl/}}, which contains all buildings in the Netherlands with detailed roofs~\citep{Peters22}.

>>>>

@@

While CityJSONSeq was developed mostly for streaming large 3D city datasets, the fact that it has a much lower memory footprint and that it takes an order of magnitude less time to process (for some local operations) makes it an attractive alternative to CityJSON for several use-cases.

It should be noticed that the CityJSON specification does not prescribe the storage of CityJSONSeq, only the structure of a CityJSONSeq stream.
In practice, CityJSONSeq can be stored in a variety of ways, for instance in a single file, each feature in a separate file, in a database, etc.
The optimal storage solution depends on the implementing application.
As a concrete example, we have implemented CityJSONSeq in the PostgreSQL, using \emph{cjdb}~\citep{Powalka23}, to store independently one feature per row in the database.
Additionally, in order to facilitate pagination, CityJSONSeq is the return format of the 3DBAG API\footnote{\url{https://api.3dbag.nl/}}, which contains all buildings in the Netherlands with detailed roofs~\citep{Peters22}.
